Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-25 ms.tex
explain why we sample in T_2 rather than T_1
address possibility of SED normalization prior

\subsection{Sampling Parameters}
\label{sec:samp}
As discussed in $\S$\ref{sec:modeling}, our full-resolution fits
consider the ``global'' parameters $f_1$, $q_1/q_2$, $\beta_1$, $\beta_2$ to be
 fixed, while the dust spectrum normalization and dust temperature vary for
each line-of-sight. In order to predict the dust SED for a given pixel, we are 
therefore left with two remaining degrees of freedom, and must choose an 
appropriate set of two parameters to sample and thereby constrain via MCMC. To 
determine the SED normalization in each pixel, we draw samples in 
$\tilde{I}_{545}$, the broadband intensity in the 545 GHz bandpass, as defined 
in Equation \ref{eqn:inten}. With the four aforementioned global parameters 
fixed, the dust spectrum shape is determined entirely by the two dust 
temperatures, which are coupled. To constrain the dust temperatures,
 we sample in $T_2$, the hot dust temperature. For each sample in $T_2$, we 
compute the corresponding value of $T_1$, thereby specifying ($\beta$, $T$) for
both MBB components and thus fully specifying the SED shape.

@@

\begin{equation}
\label{eqn:post}
P(\tilde{I}_{545}, T_2|\{I\}) \propto \mathcal{L}(\{I\}|\tilde{I}_{545}, T_2)P(T_2)
\end{equation}

@@

This error budget is the same as that of \cite{planckdust} Equation 7. 
$c_{\nu_i}$ is the multiplicative calibration uncertainty for the intensity in 
each band. We have adopted the $c_{\nu_i}$ values listed in \cite{planckdust} 
Table 1. For the 217 GHz band, we have assigned $c_{217 GHz}$ = 0.54, from 
Table 11 of \cite{planckcalib}. $CMB$ represents the CMB intensity 
subtracted at the relevant pixel. $\delta O_{\nu_i}$ represents the uncertainty
in the offset used to tie \PLANCK~intensity to H\,\textsc{i}. We have adopted 
the  $\delta O_{\nu_i}$ values of \cite{planckdust} Table 1. $n_{\nu_i}$ 
represents the instrumental noise in the pixel of interest, and is taken to be 
the square root of the \verb|ii_cov| parameter that accompanies each 
\PLANCK~intensity map. In order to obtain reasonable fitting results at high 
latitude where the data is noisy, we include a prior on $T_2$:

@@

With $\bar{T}_2$ = 16.2 K and $\sigma_{\bar{T}_2}$ = 1.4 K. In practice we 
always perform computations using logarithms of the relevant probabilities.
%mention something about the proposal distribution at some point?

>>>>

\subsection{Sampling Parameters}
\label{sec:samp}
As discussed in $\S$\ref{sec:modeling}, our full-resolution fits
consider the ``global'' parameters $f_1$, $q_1/q_2$, $\beta_1$, $\beta_2$ to be
 fixed, while the dust spectrum normalization and dust temperature vary for
each line-of-sight. In order to predict the dust SED for a given pixel, we are 
therefore left with two remaining degrees of freedom, and must choose an 
appropriate set of two parameters to sample and thereby constrain via MCMC. To 
determine the SED normalization in each pixel, we draw samples in 
$\tilde{I}_{545}$, the broadband intensity in the 545 GHz bandpass, as defined 
in Equation \ref{eqn:inten}. With the four aforementioned global parameters 
fixed, the dust spectrum shape is determined entirely by the two dust 
temperatures, which are coupled. To constrain the dust temperatures,
 we sample in $T_2$, the hot dust temperature. For each sample in $T_2$, we 
compute the corresponding value of $T_1$, thereby specifying ($\beta$, $T$) for
both MBB components and thus fully specifying the SED shape. In principle,
we could sample in either $T_1$ or $T_2$, but have chosen to sample in $T_2$ 
because emission from this component dominates in the relatively high frequency
bands which most strongly constrain the dust temperatures.

@@

\begin{equation}
\label{eqn:post}
P(\tilde{I}_{545}, T_2|\{I\}) \propto \mathcal{L}(\{I\}|\tilde{I}_{545}, T_2)P(T_2)P(\tilde{I}_{545})
\end{equation}

@@

This error budget is the same as that of \cite{planckdust} Equation 7. 
$c_{\nu_i}$ is the multiplicative calibration uncertainty for the intensity in 
each band. We have adopted the $c_{\nu_i}$ values listed in \cite{planckdust} 
Table 1. For the 217 GHz band, we have assigned $c_{217 GHz}$ = 0.54, from 
Table 11 of \cite{planckcalib}. $CMB$ represents the CMB intensity 
subtracted at the relevant pixel. $\delta O_{\nu_i}$ represents the uncertainty
in the offset used to tie \PLANCK~intensity to H\,\textsc{i}. We have adopted 
the  $\delta O_{\nu_i}$ values of \cite{planckdust} Table 1. $n_{\nu_i}$ 
represents the instrumental noise in the pixel of interest, and is taken to be 
the square root of the \verb|ii_cov| parameter that accompanies each 
\PLANCK~intensity map.

In order to obtain reasonable fitting results at high latitude where the data 
is noisy, we include the prior on $T_2$:

@@

With $\bar{T}_2$ = 16.2 K and $\sigma_{\bar{T}_2}$ = 1.4 K. In principle, there
can also be an informative prior on $\tilde{I}_{545}$. However, we have chosen 
to assume a uniform prior on the SED normalization and, as a matter of 
notation, will omit $P(\tilde{I}_{545})$ henceforward. In practice we always 
perform computations using logarithms of the relevant probabilities.
%mention something about the proposal distribution at some point?
